Detecting changes in dispersion in COVID-19 incidence time series using a negative binomial model

### 2023-06-03 noise_covid_v2.Rmd
updates for map

![Figure 1. Empirical increase in dispersion](./figures/empirical_increase.pdf)

@@

![Figure 2A. (1) Simulated p-values for the Wald test](./figures/pvals_sim_Wald.pdf)
![(2) Simulated p-values for the Likelihood-Ratio test](./figures/pvals_sim_LRT.pdf)

@@

![Figure 2B. Mapping the Thanksgiving hypothesis across the US](./figures/map_Wald_US.pdf)

![Figure 3. Scanning for breakpoints using the LRT statistic](./figures/LRT_scan_figure.pdf)

>>>>

![Empirical increase in dispersion](./figures/empirical_increase.pdf)

@@

![Simulated p-values for the Wald test](./figures/pvals_sim_Wald.pdf)
![Simulated p-values for the Likelihood-Ratio test](./figures/pvals_sim_LRT.pdf)

@@

![Mapping the Thanksgiving hypothesis across the US](./figures/map_Wald_US.pdf)

![Scanning for breakpoints using the LRT statistic](./figures/map_diff_theta_US.pdf)
